\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-02-01 article.tex
Fixed table, added new table with values in percent
Added result section

\SubSection{Set theory}
  A \emph{set} is a collection of distinct objects. It is ``a plurality
  thought of as a unit''\cite{hausdorff:sets}. \emph{Set theory}, then, is the
  branch of mathematics that studies sets.

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- for example a sitting
  stance), technique height (low, middle, high), technique side (left arm or
  right arm, it can also be both), direction of the technique (when needed),
  primary technique type (attack, block, kick), technique group (punch,
  strike, thrust), tool group (forearm, knife hand, finger etc.), tool (inner
  forearm, outer forearm, double finger etc.), and finally motion type (normal
  motion, slow motion, consecutive motion and so on).

@@

%\Section{Results}

%What's the answer? Specifically, most good computer architecture papers
%conclude that something is so many percent faster, cheaper, smaller, or
%otherwise better than something else. Put the result there, in numbers.
%Avoid vague, hand-waving results such as ``very'', ``small'', or
%``significant.''

%If you must be vague, you are only given license to do so when you can
%talk about orders-of-magnitude improvement. There is a tension here in
%that you should not provide numbers that can be easily misinterpreted,
%but on the other hand you don't have room for all the caveats.

% Observation: Kicks happen between stances
% Tables
% Graphs

@@

% Is it possible to say anything about why there are more blocks with the left
% hand, than with the right?

@@

\begin{table}
  \centering
  \begin{tabular}{l|c|c} \hline \hline
    & Left Arm & Right Arm \\ \hline

    Blocks    & 148   & 133 \\
    Punches   &  60   &  71 \\
    Strikes   &  34   &  38 \\
    Thrusts   &  21   &  14 \\
    \hline

    \textbf{Total}   & \textbf{263}   & \textbf{256} \\
    \hline
  \end{tabular}
  \caption{Total number of techniques per arm by category.}
  %\label{tab:table1}
  \end{table}

>>>>

\SubSection{Set Theory}
  A \emph{set} is a collection of distinct objects. It is ``a plurality
  thought of as a unit''\cite{hausdorff:sets}. \emph{Set theory}, then, is the
  branch of mathematics that studies sets.

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- for example a sitting
  stance), technique height (low, middle, high), technique side (left arm or
  right arm, it can also be both), direction of the technique (when needed),
  primary technique type (attack, block, kick), technique group (block, punch,
  strike, thrust), tool group (forearm, knife hand, finger etc.), tool (inner
  forearm, outer forearm, double finger etc.), and finally motion type (normal
  motion, slow motion, consecutive motion and so on).

@@

\Section{Results}

  Our findings show that of 519 techniques, 256 (49\%) are with the left arm
  and 263 (51\%) with the right arm (Table \ref{tab:table1}). Looking at the
  total amount of techniques, only 7 techniques (about 1\%) separates an even
  distribution to both sides.

%Techniques by
  %tool group (forearm, knife hand, finger etc.)
  %tool (inner forearm, outer forearm, double finger etc.)

\SubSection{Techniques by Groups}

% what is the groups of techniques?

  Table 2: Percent distribution by arm per category
  Figures 1, 2, 3

  In terms of category distribution, there are more blocks with the left side
  than there are with the

  It is worth noting that there are more blocks with the left side than with
  the right side. That is, there are more attacks with the right arm than with
  the left arm.

\SubSection{Techniques by Patterns}

\SubSection{Techniques by Stances}

\SubSection{Techniques by Height}

\SubSection{Techniques by Motion Type}

\begin{table}
  \centering
  \begin{tabular}{l|r|r} \hline \hline
    & Left Arm & Right Arm \\ \hline

    Blocks    & 148   & 133 \\
    Punches   &  60   &  71 \\
    Strikes   &  34   &  38 \\
    Thrusts   &  14   &  21 \\
  \hline

    \textbf{Total}   & \textbf{256}   & \textbf{263} \\
    \hline
  \end{tabular}
  \caption{Number of techniques per arm by category.}
  \label{tab:table1}
  \end{table}

\begin{table}
  \centering
  \begin{tabular}{l|r|r} \hline \hline
    & Left Arm & Right Arm \\ \hline

    Blocks    &  57.81\%    &  50.57\% \\
    Punches   &  23.44\%    &  27.00\% \\
    Strikes   &  13.28\%    &  14.45\% \\
    Thrusts   &   5.47\%    &   7.98\% \\
  \hline
  \end{tabular}
  \caption{Percent distribution of techniques per arm by category.}
  \label{tab:table2}
  \end{table}

  \includegraphics[width=9cm]{all}
  \includegraphics[width=9cm]{motion_type_all}

@@

% Is it possible to say anything about why there are more blocks with the
% right hand, than with the right?

% Observation: Kicks happen between stances

% Future research
%   level of detail (ex. how each technique is divided per stance to say
%   something about what stance is more suited for a technique, or to show a
%   certain technique in a less/not used stance during step sparring to an
%   understanding of techniques beyond patterns

@@
